\documentclass[10pt,a4paper]{article}

% ---------- ATS-safe encoding and typography ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
% ATS glyph-to-unicode mapping (pdfTeX only; XeTeX/Tectonic emits Unicode natively)
\ifdefined\pdfgentounicode
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi

% ---------- Page layout ----------
\usepackage[
  a4paper,
  top=0.48in,
  bottom=0.48in,
  left=0.58in,
  right=0.58in
]{geometry}

\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{ragged2e}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\urlstyle{same}
\raggedright

% ---------- Colours ----------
\definecolor{heading}{HTML}{1F2937}
\definecolor{rulecolor}{HTML}{9CA3AF}

% ---------- Bullet styling ----------
\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=1pt,
  topsep=2pt,
  parsep=0pt,
  partopsep=0pt,
  label=\textbullet
}

\newcommand{\resumeSection}[1]{%
  \vspace{5pt}
  {\normalsize\bfseries\color{heading} #1}\par
  \vspace{1pt}
  {\color{rulecolor}\hrule height 0.4pt}
  \vspace{3pt}
}

% ---------- Reusable commands ----------
\newcommand{\resumeHeader}[1]{%
  {\fontsize{20}{22}\selectfont\bfseries\color{heading} #1}\par
}

\newcommand{\resumeTagline}[1]{%
  \vspace{0.10em}
  {\normalsize\bfseries #1}\par
}

\newcommand{\contactLine}[1]{%
  \vspace{0.18em}
  {\small #1}\par
}

\newcommand{\resumeSubheading}[4]{%
  \textbf{#1}\hfill\textbf{#2}\par
  \textit{#3}\hfill\textit{#4}\par
  \vspace{-0.15em}
}

\newcommand{\projectHeading}[2]{%
  \textbf{#1} \textbar{} \textit{#2}\par
  \vspace{-0.15em}
}

\newcommand{\skillLine}[2]{%
  \textbf{#1:} #2\par
}

\begin{document}

% ==================== HEADER ====================
\begin{center}
    {\fontsize{21}{23}\selectfont\bfseries\color{heading}
    SHIVANSH GOEL}\\[2pt]
    {\normalsize\bfseries Full Stack Developer}\\[4pt]

    {\small
    +91 9458569110
    \quad \textbar{} \quad
    \href{mailto:shivansh.goela12@gmail.com}
    {shivansh.goela12@gmail.com}
    \quad \textbar{} \quad
    Delhi, India
    \quad \textbar{} \quad
    \href{https://www.linkedin.com/in/shivansh-goel-5b2309174}
    {LinkedIn}
    \quad \textbar{} \quad
    \href{https://github.com/Tech-aficionado}
    {GitHub}
    \quad \textbar{} \quad
    \href{https://ash-labs.tech}
    {Portfolio}
    }
\end{center}

\vspace{-4pt}

% ==================== PROFESSIONAL SUMMARY ====================
\resumeSection{PROFESSIONAL SUMMARY}

Full Stack Developer building production web applications end to end with
React, Next.js, and Node.js on modern serverless infrastructure. Experienced
designing responsive user interfaces, building REST APIs and database-backed
services, and shipping features from design through deployment. Comfortable
owning both the frontend experience and the backend logic, including AI and
LLM integrations.

% ==================== TECHNICAL SKILLS ====================
\resumeSection{TECHNICAL SKILLS}

\small

\skillLine{Languages}
{JavaScript (ES6+), TypeScript, Python, SQL, HTML5, CSS3}

\skillLine{Frontend}
{React.js, React 19, Next.js, Angular, Tailwind CSS, PrimeNG, Minimal UI (MUI),
Responsive Design}

\skillLine{Backend and APIs}
{Node.js, FastAPI, REST APIs, JSON, CRUD Operations, Server-Side Rendering}

\skillLine{Databases and Storage}
{Supabase, Redis, Cloudflare D1, Caching}

\skillLine{Cloud and DevOps}
{Cloudflare Workers, Firebase Tools, Git, GitHub, Vercel-style Deployment}

\skillLine{AI Integration}
{LLM Integration, Google Gemini, RAG, Prompt Engineering, AI Security Middleware}

\normalsize

% ==================== PROFESSIONAL EXPERIENCE ====================
\resumeSection{PROFESSIONAL EXPERIENCE}

\resumeSubheading
{Full Stack Developer, Intern}
{December 2023 -- May 2025}
{Tedforge Solutions Private Limited}
{India}

\begin{itemize}
  \item Across a 17-month internship, built client-facing interfaces with
  React and Angular and developed Node.js REST APIs, turning requirements
  into responsive, production-ready features end to end.

  \item Improved MySQL and MongoDB data paths, reducing query overhead and
  making product interactions more responsive and dependable.

  \item Improved application stability by reducing reported bugs 40 percent
  through systematic debugging and refactoring, collaborating through Git and
  GitHub.
\end{itemize}

% ==================== PROJECTS ====================
\resumeSection{PROJECTS}

\projectHeading
{GhostRelay -- Privacy-First Email Aliasing Platform \href{https://ghostrelay.me}{[Live]} \href{https://github.com/Tech-aficionado/GhostRelay---Open-Source}{[Source]}}
{Next.js, React 19, Cloudflare Workers, Cloudflare D1, Resend}

\begin{itemize}
  \item Built a full stack, privacy-first email aliasing platform on
  Cloudflare's edge network, spanning the Next.js frontend, edge API routes,
  and D1 database layer.

  \item Implemented one-click alias creation with per-alias enable and
  disable controls, a responsive dashboard, and email forwarding through
  Resend while keeping the user's real address hidden.
\end{itemize}

\projectHeading
{Quizify -- AI-Powered Assessment Platform \href{https://quizify.ash-labs.tech}{[Live]}}
{Next.js, React, Supabase, Redis, Google Gemini, RAG}

\begin{itemize}
  \item Built an AI-powered assessment platform end to end, from the
  Next.js frontend and quiz UI to the Supabase data layer and server-side
  API routes that generate topic-based quizzes on demand.

  \item Implemented a RAG pipeline and a server-side AI Security Middleware
  that proxies Gemini calls with no client-side API key, and used Redis
  caching to reduce latency and cost.

  \item Applied prompt engineering for structured, schema-consistent output
  and profile contexting to tailor question difficulty per learner.
\end{itemize}

\projectHeading
{FiTrack AI -- Adaptive AI Fitness Platform \href{https://fitrack-ai.ash-labs.tech/}{[Live]}}
{Next.js, Python, Machine Learning, Supabase, Google Gemini}

\begin{itemize}
  \item Built a full stack fitness platform that unifies workout, nutrition,
  and recovery signals and adaptively adjusts workout intensity, with a
  Next.js frontend and a Python/ML-backed service.

  \item Integrated Gemini through a secure server-side proxy and delivered
  personalized, goal-aware workout guidance from each user's history.
\end{itemize}

\projectHeading
{Ziplink -- URL Shortener SaaS \href{https://ziplink.ash-labs.tech}{[Live]} \href{https://github.com/Tech-aficionado/ZipLink---Open-Source}{[Source]}}
{Next.js, Firebase, Edge Redirects}

\begin{itemize}
  \item Built a full stack URL shortener SaaS that turns long URLs into
  trackable, brand-ready links with QR-code downloads and edge redirects for
  fast, global redirection.

  \item Implemented per-link analytics and a responsive Next.js dashboard
  backed by Firebase, making every shared link measurable across campaigns.
\end{itemize}

% ==================== EDUCATION ====================
\resumeSection{EDUCATION}

\resumeSubheading
{Bachelor of Technology in Computer Science and Engineering}
{2023 -- 2027}
{COER University}
{Roorkee, India}

\begin{itemize}
  \item Relevant Coursework: Data Structures and Algorithms,
  Object-Oriented Programming, Database Management Systems, Operating
  Systems, Computer Networks, Software Engineering.
\end{itemize}

% ==================== CERTIFICATIONS ====================
\resumeSection{CERTIFICATIONS}

{\small
\textbf{Python 3.11 Programming with FastAPI Backend Framework}
\quad \textbar{} \quad
\textbf{TypeScript 5.2} -- Microsoft
\\[2pt]
\textbf{Angular 16 with TypeScript 5.2 and PrimeNG 16}
\quad \textbar{} \quad
\textbf{Onsite Technical Internship -- Trainee Software Developer (Full Stack)}
}

\end{document}
